---
title: "wordle"
author: "Karim Primov"
date: "2/8/2022"
output: html_document
---


loading libraries
```{r}
library(dplyr)
library(tidyverse)
library(sjmisc)
library(ggplot2)
library(skimr)
library(kableExtra)
```


Step1:

Creating function load_dictionary that takes single argument, "filename", which can be used to read in either of the two text files
```{r}
load_dictionary <- function(filename) {
read.delim(filename) 
}
```


Creating variables "solution_list" and "valid_list" that respectively contain vectors of possible solution words and valid words
```{r}
valid_list <- load_dictionary("collins-scrabble-words-2019.txt")
solution_list <- load_dictionary("google-10000-english-usa-no-swears.txt")
str(valid_list)
str(solution_list)
```

Step 2:

Winnowing "solution_list" to only include words included in "valid_list"
```{r}
solution_list_updated <- intersect(solution_list, valid_list)
solution_list_updated
```

Step 3:

Writing custom function pick_solution() that:
1) removes all words from solution_list that are not 5 letters in length 
2) randomly chooses a single word from those that remain 
3) then splits that word into a vector of single-character elements
```{r}
pick_solution <- function(list){
  lista = list(nchar(list) == 5)
  listb = sample(lista, 1)
  str_extract_all(listb, boundary("character"))[[1]]
}
solution <- pick_solution(solution_list_updated)
```



















































