---
title: "wordle"
author: "Karim Primov"
date: "2/8/2022"
output: html_document
---


loading libraries
```{r}
library(dplyr)
library(tidyverse)
library(sjmisc)
library(ggplot2)
library(skimr)
library(kableExtra)
```


Step1:

Creating function load_dictionary that takes single argument, "filename", which can be used to read in either of the two text files
```{r}
load_dictionary <- function(filename) {
a = read.delim(filename) 
return(a$words) 
#a$words
}
```


Creating variables "solution_list" and "valid_list" that respectively contain vectors of possible solution words and valid words
```{r}
valid_list <- load_dictionary("collins-scrabble-words-2019.txt")
solution_list <- load_dictionary("google-10000-english-usa-no-swears.txt")
str(valid_list)
str(solution_list)
```

Step 2:

Winnowing "solution_list" to only include words included in "valid_list"
```{r}
solution_list_updated <- intersect(solution_list, valid_list)
solution_list_updated
```

Step 3:

Writing custom function pick_solution() that:
1) removes all words from solution_list that are not 5 letters in length 
2) randomly chooses a single word from those that remain 
3) then splits that word into a vector of single-character elements
```{r}
pick_solution <- function(solv.list){
  lista = solv.list[nchar(solv.list) == 5]
  listb = sample(lista, 1)
  str_extract_all(listb, boundary("character"))[[1]]
  return(str_extract_all(listb, boundary("character"))[[1]])
}
solution <- pick_solution(solution_list_updated)
```


Step 4:

Comparing guess to the solution word and generate necessary feedback
```{r}
helper_function <- function(guess, solution){
  #can just use "guess" and "solution" in helper function without need to split them into vectors 
  #setting up for loop going through each letter in "guess"
output.variable = c()
i = 1                                  #setting i to 1
  while (i <= length(guess)){ 
    j = 1
    while (j <= length(solution)){   
      if (guess[i] == solution[j]){      #if the ith letter in guess equal to the jth letter in solution
        if (i == j){                     #e.g. seeing if the letters are at the same position within both the guess and solution vector
          output.variable[i] = "*"
        }
          else {
            output.variable[i] = "+"
          }
        solution = solution[-j]          #e.g. removing A from solution word "PLANE" when A is found in guess "APPLE" 
        i = i + 1
        j = 1
      }
      else{                              
        if (j == length(solution)){
          output.variable[i] = "-"
          i = i + 1
          j = j + 1
        }
      else{
        j = j + 1
      }
    }
 }
    return(output.variable)
 }
}
  
```


Writing play_wordle function
```{r}
play_wordle <- function(solution, valid_list, num_guesses=6){
  print("You have 6 chances to guess a word of length 5")
  print("Letters left:")
  print(toString(LETTERS))
  guess_count <- 1
  while (guess_count <= num_guesses) {
    guess <- readline(paste0("Enter guess number " , guess_count, " then press Enter: "))
    guess <- toupper(guess)
    if (guess %in% valid_list){ 
      guess.str_extract <- str_extract_all(guess, boundary("character"))[[1]]    #split the guess word into a vector of length 5
      #if guess is within the valid list 
      if (length(guess.str_extract) == 5){
        print("valid guess")
        #and if guess is 5 letters long 
        helper_function(guess.str_extract, solution)                               #use helper function to evaluate guess vs. solution
        if (guess.str_extract == solution){                                        #if helper function's output == solution
          print("You win!")}                                                      #then player wins the game
          else{                                                                   #otherwise,
            if (guess_count <=6){                                                 #if the number of guesses left is still less than 6
              guess <- readline("Enter guess number, then press Enter: ")         #then player has another chance to guess
            }
            else{                                                                #otherwise,
              print("You lose")                                                  #print "You lose"
            }
          }
      }
    }
      else{
          print("This is not a valid guess")
          guess <- readline(paste0("Enter guess number " , guess_count, " then press Enter: "))
      }
    guess_count <- guess_count+1
  }
    
  #else guess
}

```

play_wordle(solution, valid_list, num_guesses=6)


